Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-08 doc/PRF2022/PRF_main.tex

\begin{abstract}
% insert abstract here
%
%{\bf To do list:}
%
%Unbouned Flow: 
%\begin{enumerate}
%\item $N_b=60$ self-assembly/relaxation runs with all 3 boundary
%  conditions using $N=24$ points per particle (FIG. 2). Energy profiles
%    in a log-log plot (FIG. 3) ($E(t)$ or $\Delta E(t)$ v.s. time).
%
%\item $N_b=198$ relaxation runs with all 3 boundary conditions using $N=24$ points per particle.
%Add energy profiles to check local/absolute minimum. Superimpose these
%    energies on Figure 3, but scale the energies by the number of Janus
%    particles so that it is ``energy per particle"
%
%\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 5), convergence tests using $N=16$ and $N=24$ are not yet verified. 
%Compare results using $N_b=24$ with the current FIG 4. (d). Revise FIG. 5 with more details. 
%
%\item Use particle/checker board alignment and/or aspect ratio to identify the critical shear rate for phase separation.
%
%\item $N_b=60$ structures in a Taylor-Green flow (FIG. 7-8). Add more frames for further comparison between values of flow strength $V_0$.
%\end{enumerate}
%
%
%{\bf May do list:}
%Channel Flow: 
%\begin{enumerate}
%\item Convergence tests for $N_b=25$ vesicle in a narrow channel.  Add energy profile.
%
%\item Convergence tests for $N_b=40$ multi-lamellar structure in a narrow channel. Add energy profile.
%
%\end{enumerate}

\end{abstract}

@@

To see the effect of the shift parameter $b$, we simulate the dynamics of
198 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
Three distinct configurations emerge:
(i) bilayers for $b = 1$, 
(ii) multilamellar for $b = 2$, and 
(iii) striated for $b = 0$.

Case (i) with $b = 1$, mimicks an amphiphilic particle.
The boundary condition $g$ is everywhere nonnegative,
takes the value $0$ on the
hydrophilic head,
and takes the maximum value $a$ on the
hydrophobic tail. 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)).

In case (ii) with $b = 1$, the boundary condition is positive everywhere.
It takes the maximum value $3a$ on tail and the
minimum value $a$ on the head side. 
Both sides of the Janus particle are hydrophobic but
moreso on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers also adhere to one another 
forming multilamella structures. Figure~\ref{fig:relax}(c), for example, shows a
multilamellar structure with 2 layers.
At equilibrium, the number of folds depends primarily on the number of particles.

A water structure with
positive/negative charge is possible in case (iii), $b = 0$
\cite{MaRa76, Ma77}.
Here, the head repels the tail of other particles
and the particles initially form chains with their directors perpendicular
to the length of the chain.  
The chains form stria
where the particles lie on a 
grid and the orientations alternate between layers (Figure~\ref{fig:relax}(d)).

@@

\begin{figure}
  \begin{center}
%  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
%\includegraphics[width=0.49\textwidth]{relax_E.pdf}
%\includegraphics[width=0.49\textwidth]{relax_LOP.pdf} 
\includegraphics[width=1.0\textwidth]{relax_E_LOP.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  A:  The free energy \eqref{eq:free_energy} decreases
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations as shown in Figure \ref{fig:relax}b--d, respectively.
    The black curves are the energies for the $N_b=60$ cases and  
    the red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. 
    The curve styles are identical to the ones in panel A.
    The near-equilibrium configurations depend on the initial configuration and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trend in self-assembly in term of the local order parameter. The results of the striated configuration depend on the initial setup.
  }
\end{figure}

@@

@@

\begin{figure}
  \begin{center}
      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
   \includegraphics[width=0.22\textwidth]{VS_3.pdf}\\
         \includegraphics[width=0.22\textwidth]{BS_0.pdf}
      \includegraphics[width=0.22\textwidth]{BS_1.pdf}
   \includegraphics[width=0.22\textwidth]{BS_2.pdf}
   \includegraphics[width=0.22\textwidth]{BS_3.pdf}
%   Panels (e)-(f) same but for non-vesicle initial configuration
  \end{center}
  \caption{
    \label{fig:BC1_shear_flow}
    The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=500$). The streamlines are plotted in the background. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
      \includegraphics[width=0.3\textwidth]{BS_E.pdf}
   \includegraphics[width=0.3\textwidth]{BS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{BS_MSD.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$. Shear rates are $\dot\gamma=\{0.05, 0.0655, 0.75\}$. The shear rate $\dot\gamma = 0.0655$ are picked from ~\cite{Fu2022_JFM} where it is known to be the critical shear rate for ruptures and the trend is clearly distinguished from all three measures. For the bilayer configurations, as shown in Fig~\ref{fig:relax}, multiple bialyer structures are placed in shear flows. The supplementary movies show that a slower shear flow results menbrane fusions and $\tilde{S}_2(t)$ increases in the long run.
     }
\end{figure}

\subsection{Boundary condition (i):   bilayer configurations}
The vesicle in a shear flow undergoes the familiar tank-treading deformation.
Our previous paper \cite{Fu2022_JFM} studied the geometry,
intermonolayer slip, and critical shear rates $\gamma^*$
for vesicles comprised of amphiphilic Janus particles.

The vesicle is subject to a shear background flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma ({\bf e}_y\cdot\xx){\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the shear rate. Figure~\ref{fig:shear_1} (a)--(c)
shows snapshots of the vesicle when $\dot\gamma= ... $ is
below the critical shear rate $\dot \gamma_* = ...$
Here, the free energy and order parameter are more or less constant
(Figure \ref{fig:BC1_shear}ab, solid curves).  The is a slight upward shift
in $d(t)$ (Figure \ref{fig:BC1_shear}c, solid curve) due to relative
displacement as the two leaflets slide past one another.

%\begin{figure}
%\caption{\label{fig:ves_shear} A vesicle in shear flow}
%\end{figure}
%\begin{figure}
%\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
%\end{figure}

In, Figure~\ref{fig:shear_2} (a)--(c), 
$\dot\gamma= ...$ is above the critical shear rate,
and there is a jump in energy (Figure \ref{fig:BC1_shear}a, dashed curve)
due to the breaking of the vesicle into two components.  
There is greater variation in the order parameter $\tilde{S}_2(t)$ as well
with a baseline value around $0.7$
(Figure \ref{fig:BC1_shear}b, dashed curve).The oscillations occur due to the
orbit of the two bilayer components, and $\tilde{S}_2(t)$ increases
to about $0.9$ when the components are nearly parallel and slide past one another.
Positional order, however, diverges since the two component configuration
is uncorrelated to the initial circular configuration (Figure \ref{fig:BC1_shear}c, dashed curve).

%

The Taylor-Green (TG) background flow is
\begin{equation}
  \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
  +\sin({\bf e}_x\cdot\xx/l)\cos({\bf e}_y\cdot\xx/l){\bf e}_y\right).
\end{equation}
where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. 
%

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{VTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{VTG_3.pdf} \\
      \includegraphics[width=0.22\textwidth]{BTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{BTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{BTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{BTG_3.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG_flow} The figure shows a vesicle in Taylor-Green flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=600$) 
    and the multiple component bilayers in Taylor-Green flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=200$). The streamlines are plotted in the background.
  }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}\\
  \includegraphics[width=0.3\textwidth]{BTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{BTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{BTG_MSD.pdf}
  \end{center}
\caption{\label{fig:BC1_TG} A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$. The result indicates that the highest flow strength ($V_0=0.2$) makes the vesicle (top row) rupture within a short period of time and the energy rapidly increases. As expected, the local order parameter drops and the MSD increases. For bilayer structure (bottom row), for $V_0=0.15$ and $V_0 = 0.2$, the energy gradually increases over the time but the other two measures do not have  a clear trend.}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{VTG_Scale_0.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_Scale_1.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_Scale_2.pdf} 
    \includegraphics[width=0.22\textwidth]{VTG_Scale_3.pdf}
      \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_Scale_flow} With $V_0=0.1$, panels (a)-(d) show the configurations with streamlines when a vesicle is in Taylor-Green flow at $t=1000$ and $l= 1,2,3,4$, respectively.}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{VTG_Len.pdf}
  \includegraphics[width=0.4\textwidth]{VTG_Area.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:VTG_AreaLen} Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied. The enclosed area calculated from the bilayer midplane decreases over time and the total length measured from the midplane remains nearly constant with small magnitude of oscillations. }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{MS_0.pdf}
  \includegraphics[width=0.22\textwidth]{MS_1.pdf}
  \includegraphics[width=0.22\textwidth]{MS_2.pdf} 
    \includegraphics[width=0.22\textwidth]{MS_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_shear_flow} Multi-lamellar stracture in shear flows. The insets of Fig~\ref{fig:relax}c is used for panels (a). Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=600$, respecitively. The streamlines are plotted in the background.}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{MS_E.pdf}
   \includegraphics[width=0.3\textwidth]{MS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{MS_MSD.pdf}
  \end{center}
      \caption{\label{fig:BC2_shear} 
      A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$. For this set of simulations, the local order parameter is a good indicator for tracking the rupture or structure separations. Moreover, all three measure show that the energy, orderparameter, and MSD increase as shear rate increases.}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{MTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{MTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{MTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{MTG_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_TG_flow} Multi-lamellar stracture in Taylor-Green flows. The insets of Fig~\ref{fig:relax}c is used for panels (a). Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.1, 0.15, 0.2\}$ at $t=600$, respecitively. The streamlines are plotted in the background. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{MTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{MTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{MTG_MSD.pdf}
  \end{center}
    \caption{\label{fig:BC2_TG}  A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$. The energy profile when $V_0=0.2$ has an increasing trend that results a large deformation after a period of time. Since the flow strengths for all cases are not strong enough, the convergent MSD represents that the rupture does not occur before $t=1000$.}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{CS_0.pdf}
  \includegraphics[width=0.22\textwidth]{CS_1.pdf}
  \includegraphics[width=0.22\textwidth]{CS_2.pdf} 
    \includegraphics[width=0.22\textwidth]{CS_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC3_shear_flow} A striated configuration in shear flows where the streamlines are plotted in the background. Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$ at $t=100$, respectively. 
  }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{CS_E.pdf}
   \includegraphics[width=0.3\textwidth]{CS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{CS_MSD.pdf}
  \end{center}
\caption{\label{fig:BC3_shear} A striated configuration in shear flows with shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$. The energy profile, order parameter, and MSD for the case $\dot\gamma=0.15$ show that a rupture occurs during the simulation. For other two cases, all measures remain nearly constant. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{CTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{CTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{CTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{CTG_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC3_TG_flow}  A striated configuration in shear flows where the streamlines are plotted in the background. Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the flow strengths $V_0=\{0.2, 0.25, 0.3\}$ at $t=400$, respectively. . }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{CTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{CTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{CTG_MSD.pdf}
  \end{center}
\caption{\label{fig:BC3_TG} A striated configuration in Taylor-Green flows with flow strengths $V_0=\{0.2, 0.25, 0.3\}$.   }
\end{figure}

>>>>

\begin{abstract}
% insert abstract here
\end{abstract}

@@

To see the effect of the shift parameter $b$, we simulate the dynamics of
198 particles and 60 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
Three distinct configurations emerge:
(i) bilayers for $b = 1$, 
(ii) multilamellar for $b = 2$, and 
(iii) striated for $b = 0$.

Figure~\ref{fig:relax}a shows the initial configurations with orientations of 198-particle and 60- particle cases. 
Case (i) with $b = 1$, mimicks an amphiphilic particle.
The boundary condition $g$ is everywhere nonnegative,
takes the value $0$ on the
hydrophilic head,
and takes the maximum value $a$ on the
hydrophobic tail. 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)). The inset shows the equilibrium 
state for 60-particle run that forms multiple bilayers with a vesicle like structure.

In case (ii) with $b = 1$, the boundary condition is positive everywhere.
It takes the maximum value $3a$ on tail and the
minimum value $a$ on the head side. 
Both sides of the Janus particle are hydrophobic but
moreso on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers also adhere to one another 
forming multilamella structures. Figure~\ref{fig:relax}(c), for example, shows a
multilamellar structure with multiple layers.
At equilibrium, the number of folds depends primarily on the number of particles.
In addition, the inset provides a 3-fold structure when there are 60 particles.

A water structure with
positive/negative charge is possible in case (iii), $b = 0$
\cite{MaRa76, Ma77}.
Here, the head repels the tail of other particles
and the particles initially form chains with their directors perpendicular
to the length of the chain.  
The chains form stria
where the particles lie on a 
grid and the orientations alternate between layers (Figure~\ref{fig:relax}(d)). We observe that 
when the number of particles is fewer, there is only single alternating pattern in particle orientations. Larger number of particles results two different patterns as shown in the figure.

@@

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  A:  The free energy \eqref{eq:free_energy} decreases
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations as shown in Figure \ref{fig:relax}b--d, respectively.
    The black curves are the energies for the $N_b=60$ cases and  
    the red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. 
    The curve styles are identical to the ones in panel A.
    The near-equilibrium configurations depend on the initial configuration and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trend in self-assembly in term of the local order parameter. The results of the striated configuration depend on the initial setup.
  }
\end{figure}

Figure~\ref{fig:relax_energy}a tracks the free energy profiles for all relaxation runs. For 198-particle cases, we normalized the energies by 60/198 and the results show that all energies decrease with good agreements in all boundary conditions. Figure~\ref{fig:relax_energy}b 
measures the orientational order parameter $\tilde{S}_2$. Both bilayer and multilamellar 
structures have similar trends in small and large systems. The aggregation for striated configurations may have a significant difference when the number of particles is varied.

%%%%%%%

@@

\subsection{Boundary condition (i):   bilayer configurations}

\begin{figure}
  \begin{center}
   \includegraphics[width=1.0\textwidth]{Figures/Figure3.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=500$). The streamlines are plotted in the background. }
\end{figure}

The bilayer is subject to a shear background flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma ({\bf e}_y\cdot\xx){\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the shear rate. 
Figure~\ref{fig:BC1_shear} (a)--(c)
shows snapshots of the vesicle when $\dot\gamma= 0.05,0.075,0.01$.
The free energies (Figure~\ref{fig:BC1_shear}d) are relatively constant and 
lower shear rate results a smaller orientational parameter (Figure~\ref{fig:BC1_shear}e). The supplementary movies show that these bilayers merge and form a work-like shape in higher 
shear flows. Figure~\ref{fig:BC1_shear}f shows that the strain parameter diverges when 
the shear rate is large enough.

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
  \end{center}
  \caption{
    \label{fig:Ves_shear}
    Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$. Shear rates are $\dot\gamma=\{0.05, 0.0655, 0.75\}$. The shear rate $\dot\gamma = 0.0655$ are picked from ~\cite{Fu2022_JFM} where it is known to be the critical shear rate for ruptures and the trend is clearly distinguished from all three measures. For the bilayer configurations, as shown in Fig~\ref{fig:relax}, multiple bialyer structures are placed in shear flows. The supplementary movies show that a slower shear flow results menbrane fusions and $\tilde{S}_2(t)$ increases in the long run.
     }
\end{figure}

In Figure~\ref{fig:Ves_shear} (a)--(c), the vesicle in a shear flow undergoes the familiar tank-treading deformation. 
Our previous paper \cite{Fu2022_JFM} studied the geometry,
intermonolayer slip, and critical shear rates $\gamma^*=0.066$
for vesicles comprised of amphiphilic Janus particles. 
Here $\dot\gamma=0.05, 0.066, 0.075$ and there are jumps in energies (Figure \ref{fig:Ves_shear}d, long and short dashed curves) due to the breaking of the vesicle into two
components. There is greater variation in the order parameter $\tilde{S}_2(t)$ as well
with a baseline value around $0.7$
(Figure \ref{fig:Ves_shear}e, dashed curve).
The oscillations occur due to the orbit of the two bilayer components, and $\tilde{S}_2(t)$ increases to about $0.9$ when the components are nearly parallel and slide past one another.
For the lowest shear rate case, it has nearly perfect orientational parameter due to the steady tank-treading motion.
Positional order, however, diverges since the two component configuration
is uncorrelated to the initial circular configuration (Figure \ref{fig:Ves_shear}f, dashed curve).

%%%%%%%

The Taylor-Green (TG) background flow is
\begin{equation}
\label{eq:tg_flow}
  \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
  +\sin({\bf e}_x\cdot\xx/l)\cos({\bf e}_y\cdot\xx/l){\bf e}_y\right).
\end{equation}
where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. The default parameter
$l=2$ is used through this work.
%

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG} The figure shows a vesicle in Taylor-Green flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=600$) 
    and the multiple component bilayers in Taylor-Green flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=200$). The streamlines are plotted in the background.
  }
\end{figure}

Figure~\ref{fig:BC1_TG}a--c are the snapshots when $V_0=0.1,0.15,0.2$, respectively.
This initial configuration in TG flow encounters a number of fusion but there is no clear trend for
all measures with respect to the flow strengths.

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
  \end{center}
\caption{\label{fig:ves_TG} A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$. The result indicates that the highest flow strength ($V_0=0.2$) makes the vesicle (top row) rupture within a short period of time and the energy rapidly increases. As expected, the local order parameter drops and the MSD increases. For bilayer structure (bottom row), for $V_0=0.15$ and $V_0 = 0.2$, the energy gradually increases over the time but the other two measures do not have  a clear trend.}
\end{figure}

For a vesicle in a Taylor-Green flow, Figure~\ref{fig:ves_TG}a--c are configurations at $t=0.2 \mu$s where $V_0=0.1,0.15,0.2$. Figure~\ref{fig:ves_TG}d--f indicates that the rupture occurs when the energy and strain parameter are significant larger and the orientational parameter is much lower than other cases.

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure7.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)-(d) show the configurations with streamlines when a vesicle is in Taylor-Green flow at $t=1000$ and $l= 1,2,3,4$, respectively.
  Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied. The enclosed area calculated from the bilayer midplane decreases over time and the total length measured from the midplane remains nearly constant with small magnitude of oscillations.
  }
\end{figure}

We vary the cell size by tuning the parameter $l$ in \eqref{eq:tg_flow}.  Figure~\ref{fig:BTG_Scale}a--d show the deformation of a vesicle in a Taylor-Green flow when $V_0=0.1$ and arrows indicate rotating directions. Figure~\ref{fig:BTG_Scale}e presents that the area $A/A_0$ decreases during the simulations and the inset shows constant total lengths $L/L_0$ for all cases where $A_0$ and $L_0$ are initial enclose area and midplane length.
%A/A0 plot with no monotonic trend.
One interesting finding is that the number of cells affects the directions of structure rotation.

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure8.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_shear}   Multi-lamellar stracture in shear flows. The insets of Fig~\ref{fig:relax}c is used for panels (a). Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=600$, respecitively. The streamlines are plotted in the background.  A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$. For this set of simulations, the local order parameter is a good indicator for tracking the rupture or structure separations. Moreover, all three measure show that the energy, orderparameter, and MSD increase as shear rate increases.
       }
\end{figure}

We place a 60-particle multilamellar configuration (inset of Figure~\ref{fig:BC2_shear}a) in shear flows where $\dot\gamma=0.05, 0.1, 0.15$. Quantities such as energies, orientational parameter, and positional parameter (Figure~\ref{fig:BC2_shear}d--f) follow the same trend where they increases as shear rate increases. 
Comparing with bilayer structures, Figure~\ref{fig:BC2_shear}a--c demonstrate that the multilamellar ones are more rigid in shear flow and the rupture phenomenon can be observed 
when the shear rate is high enough.

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure9.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_TG} Multi-lamellar stracture in Taylor-Green flows. The insets of Fig~\ref{fig:relax}c is used for panels (a). Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.1, 0.15, 0.2\}$ at $t=600$, respecitively. The streamlines are plotted in the background. A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$. The energy profile when $V_0=0.2$ has an increasing trend that results a large deformation after a period of time. Since the flow strengths for all cases are not strong enough, the convergent MSD represents that the rupture does not occur before $t=1000$.
  }
\end{figure}

For multilamellar structure in a Taylor-Green flow, as shown in Figure~\ref{fig:BC2_TG}a--b, lower flow strengths such as $V_0=0.1,0.15$ do not reach a critical flow rate for structural disorder. 
When $V_0=0.2$ (Figure~\ref{fig:BC2_TG}c), the flow is strong enough to separate the structure
into multiple groups within the cells. In all deformation measures, a similar trend in shear flow case is observed, see Figure~\ref{fig:BC2_TG}d--f.

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure10.pdf}        
  \end{center}
      \caption{\label{fig:BC3_shear}  A striated configuration in shear flows where the streamlines are plotted in the background. Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$ at $t=100$, respectively. 
       A striated configuration in shear flows with shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$. The energy profile, order parameter, and MSD for the case $\dot\gamma=0.15$ show that a rupture occurs during the simulation. For other two cases, all measures remain nearly constant.
    }
\end{figure}

We place the striated configuration in a shear flow when $\dot\gamma=0.1, 0.125, 0.15$ and 
the snapshots at $t=0.1 \mu$s are shown in Figure~\ref{fig:BC3_shear}a--c.
Break-up deformation measures (igure~\ref{fig:BC3_shear}d--f) are similar to vesicle in shear flow case. Notably, for low shear rates, oscillatory behaviours are investigated in energies, orientational and positional parameters.

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure11.pdf}            
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC3_TG} A striated configuration in Taylor-Green flows where the streamlines are plotted in the background. Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the flow strengths $V_0=\{0.2, 0.25, 0.3\}$ at $t=400$, respectively.}
\end{figure}

For a striated configuration in a Taylor-Green flow, numerical experiments have shown that one needs to choose relative higher flow strengths than other boundary conditions to reach structural disorder. Figure~\ref{fig:BC3_TG}a--c are configurations for $V_0=0.2, 0.25, 0.3$ at $t=0.4 \mu$s.
Figure~\ref{fig:BC3_TG}d--f show that the threshold for having clear rupture is between $V_0=0.2$ and $V_0=0.25$ and a huge jump in measures occurs soon after the flow is turned on.
